Competing Bandits: \\ The Perils of Exploration under Competition

### 2018-11-06 paper/content/inverted_u.tex
Edits in Sec4.

\gaedit{
\xhdr{Welfare}

\swedit{We also study the effects the competition has on the consumer welfare---the cumulative rewards received by the users over time.}

@@

\swedit{For our purpose, it will be clearer to look at \emph{market
    regret}: the difference between the cumulative mean rewards
  achieved by taking the best action over all rounds and the
  cumulative mean rewards received by the agents. (Hence smaller
  regret means higher welfare.)}

Figure \ref{eq_regret} displays the \swedit{market regret (average
  over multiple runs)} under different levels of competitions,
assuming both firms playing their equilibrium strategies. Consumers are \textit{better off} in the temporary monopoly case than in
the duopoly case. However, this was expected from the fact that the incumbent is incentivized to play \TS. The welfare in the temporary monopoly case is close to the welfare to having a single firm playing
\TS. \gaedit{We also observe that monopoly and duopoly achieve similar welfare, with monopoly being marginally better than duopoly.}

@@

\begin{finding}
\textit{When all firms in the market deploy \DG, welfare is weakly decreasing as the number of firms in the market decreases.}
\end{finding}
\swedit{To study this phenomenon further, we go beyond the two-firm
  setting and simulate the game an increasing number of firms playing
  \DG.} Figure \ref{many_firm_welfare} reports the average welfare
across these simulations. Welfare not only does not get better,
\textit{but is weakly worse} as we increase the number of
firms. Correspondingly, we track the average \Eeog in each of the
simulations and notice that it is \textit{increasing} as the number of
firms increases. As we increase the number of firms, a single
individual firm gets fewer consumers for learning as consumers switch
between firms more often. Additionally, bad luck with rewards or arm
selection is punished even more harshly as we increase the number of
firms. This further strengthens the intuition from our previous
result, which is that learning may be hard under competition since
exploration and mistakes are punished harshly but are necessary for
learning.}

>>>>

\xhdr{Welfare.}
\asedit{We study the effects of competition on consumer welfare: the total reward collected by the users over time. Rather than welfare directly, we find it more lucid to consider
\emph{market regret}: 
\[ \textstyle T\, \max_a \mu(a) - \sum_{t\in [T]} \mu(a_t), \]
where $a_t$ is the arm chosen by agent $t$. This is a standard performance measure in the literature on multi-armed bandits. Note that smaller regret means higher welfare.}

@@

\asedit{We assume that both firms play their respective equilibrium strategies for the corresponding competition level. As discussed previously, these are:}
\ascomment{Guy, pls fill in, and refer to the corresponding findings.}

Figure \ref{eq_regret} displays the \swedit{market regret (average
  over multiple runs)} under different levels of competition.
Consumers are \textit{better off} in the temporary monopoly case than in
the duopoly case. However, this was expected from the fact that the incumbent is incentivized to play \TS. The welfare in the temporary monopoly case is close to the welfare to having a single firm playing
\TS. \gaedit{We also observe that monopoly and duopoly achieve similar welfare, with monopoly being marginally better than duopoly.}

@@

\begin{finding}
\textit{When all firms in the market deploy \DG, welfare is weakly decreasing as the number of firms in the market decreases.}
\end{finding}
\swedit{To study this phenomenon further, we go beyond the two-firm
  setting and simulate the game an increasing number of firms playing
  \DG.} Figure \ref{many_firm_welfare} reports the average welfare
across these simulations. Welfare not only does not get better,
\textit{but is weakly worse} as we increase the number of
firms. Correspondingly, we track the average \Eeog in each of the
simulations and notice that it is \textit{increasing} as the number of
firms increases. As we increase the number of firms, a single
individual firm gets fewer consumers for learning as consumers switch
between firms more often. Additionally, bad luck with rewards or arm
selection is punished even more harshly as we increase the number of
firms. This further strengthens the intuition from our previous
result, which is that learning may be hard under competition since
exploration and mistakes are punished harshly but are necessary for
learning.
